Databrary: A digital data library for sharing research video

### 2015-01-15 jcdl-15/paper.tex
basic outline

Permission to make digital or hard copies of all or part of this work
for personal or classroom use is granted without fee provided that
copies are not made or distributed for profit or commercial advantage
and that copies bear this notice and the full citation on the first
page. To copy otherwise, or republish, to post on servers or to
redistribute to lists, requires prior specific permission and/or a fee.

>>>>

\subsection{Video-based human research data}

\subsection{Discovering and re-purposing data}

\section{The ``Session''}

\section{Organizing and documenting collections}

\section{Collecting and annotating temporal data}

\section{Open Problems}
